Interactive Checks for Coordination Avoidance

### 2019-08-22 doc/vldb_slides/sections/iclosure.tex
Finished slide revisions.

\begin{frame}
  \Huge
  \begin{center}
    Reasoning about reachable states is hard.
  \end{center}

@@

    Instead of reasoning about invariant confluence directly then, let's look
    at a sufficient condition for invariant confluence called invariant
    closure. \\[12pt]
  }
\end{frame}

@@

  \note{%
    Invariant closure is a sufficient condition for invariant confluence. I'll
    refer you to the paper for the proof, but it's a very simple proof.
  }
\end{frame}

@@

@@

\begin{frame}
  \Large
  \[
    \text{invariant closure}
    \xLeftarrow{\phantom{a}?\phantom{a}}
    \text{invariant confluence}
  \]

@@

\begin{frame}
  \Large
  \[
    \text{invariant closure} \centernot\impliedby \text{invariant confluence}
  \]

@@

>>>>

\begin{frame}
  \begin{center}
    \begin{tikzpicture}[xscale=3, yscale=2]
      \node (confluence) at (2, 0) {\Large invariant confluence};
      \pause

      \node (hard) at (2, 1) {hard to check :(};
      \draw[-latex, thick] (hard) to (confluence);
      \pause

      \node (closure) at (0, 0) {\Large invariant closure};
      \node at ($(confluence)!0.5!(closure)$) {\Large $\implies$};
      \pause

      \node (easy) at (0, 1) {easy to check :)};
      \draw[-latex, thick] (easy) to (closure);
    \end{tikzpicture}
  \end{center}

@@

    Instead of reasoning about invariant confluence directly then, we'll look
    at a sufficient condition for invariant confluence called invariant
    closure. \\[12pt]

    Unlike invariant confluence, we'll see that invariant closure is easy to
    check. \\[12pt]
  }
\end{frame}

@@

  \note{%
    As I mentioned earlier, invariant closure is a sufficient condition for
    invariant confluence. I'll refer you to the paper for the proof, but it's a
    very simple proof.
  }
\end{frame}

@@

\begin{frame}
  \begin{center}
    \begin{tikzpicture}[xscale=3, yscale=2]
      \node (confluence) at (2, 0) {\Large invariant confluence};
      \node (closure) at (0, 0) {\Large invariant closure};
      \node at ($(confluence)!0.5!(closure)$) {\Large $\implies$};
      \node (hard) at (2, 1) {hard to check :(};
      \draw[-latex, thick] (hard) to (confluence);
      \node (easy) at (0, 1) {easy to check :)};
      \draw[-latex, thick] (easy) to (closure);
    \end{tikzpicture}
  \end{center}

@@

\begin{frame}
  \Large
  \[
    \text{invariant closure}
    \xLeftarrow{\phantom{aa}?\phantom{aa}}
    \text{invariant confluence}
  \]

@@

\begin{frame}
  \begin{center}
    \begin{tikzpicture}[xscale=3, yscale=2]
      \node (confluence) at (2, 0) {\Large invariant confluence};
      \node (closure) at (0, 0) {\Large invariant closure};
      \node at ($(confluence)!0.5!(closure)$) {\Large $\centernot\impliedby$};
      \node (hard) at (2, 1) {hard to check :(};
      \draw[-latex, thick] (hard) to (confluence);
      \node (easy) at (0, 1) {easy to check :)};
      \draw[-latex, thick] (easy) to (closure);
    \end{tikzpicture}
  \end{center}

@@

\begin{frame}
  \Large
  If $I$ is a subset of reachable states, then
  \begin{center}
    \begin{tikzpicture}[xscale=3, yscale=2]
      \node (confluence) at (2, 0) {\Large invariant confluence};
      \node (closure) at (0, 0) {\Large invariant closure};
      \node at ($(confluence)!0.5!(closure)$) {\Large $\iff$};
      \node (hard) at (2, 1) {hard to check :(};
      \draw[-latex, thick] (hard) to (confluence);
      \node (easy) at (0, 1) {easy to check :)};
      \draw[-latex, thick] (easy) to (closure);
    \end{tikzpicture}
  \end{center}

  \note{%
    This is good news. Invariant confluence is hard to check, but invariant
    closure is easy to check. And when the invariant is a subset of the
    reachable states, the two are equivalent. In this case, invariant
    confluence also becomes easy to check.
  }
\end{frame}
